\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-04-22 sections/results.tex
Change: Update TA section with supplementary info

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generated co-occurrence networks using all possible combinations of methods and estimated the variability in the networks due to each choice (Figure \ref{fig:figure2}A).
  This analysis and all subsequent analysis, unless explicitly mentioned, are performed on all the samples in the fecal microbiome transplant study.
  The networks are filtered on both association strength (0.1) and pvalue (0.05, only correlation methods) before the networks are subjected to the analyses.
  The effects of various steps on the final co-occurrence network is estimated by building a linear model of the edges of the network as a function the various step in the analysis pipeline (see Methods).
  Figure \ref{fig:figure2}A, shows the percentage of total variation among the co-occurrence networks due to the different steps of the pipeline.
  The TA step, more specifically, the choice of 16S reference database contributes the most ($\sim65.4\%$) to the variation in the networks, followed by the OP step ($\sim26.8\%$).
  This result highlights the importance of the taxonomy assignment step in the 16S data analysis workflow, implying that a change in the reference database will result in drastically different inferred networks.
  % TODO: Verify this: Figure S4
  The reason for this seems to derive from the mislabelling of constitutive taxa that are present in high abundance in the community, which drastically alter the nodes and hence the underlying network topology.
  In fact the variability induced by taxonomy assignment is much more significant than that due to the variability induced based on how the reference sequences themselves are identified (in the DC step).
  The residual variation (Figure \ref{fig:figure2}A) can be seen as an artifact that arises when multiple steps are changed at the same time, however this is small.

@@

  After assigning all the representative sequences to taxonomies we perform a pairwise comparison of the similarity between the top 100 assignments (by abundance) from different databases at every taxonomic level (Figure~\ref{fig:figure4}B).
  The assignments beyond Family level (Family, Genus and Species) are very dissimilar with $<45\%$ similarity between any pair of databases.
  The matches and mismatches in the assignments from all three databases are comparable, with \ac{ncbi} and SILVA being the most similar across most of the taxonomic levels, followed closed by \ac{gg} vs. SILVA.
  However, the number of mismatches for taxonomy assignments beyond the Genus level (Genus, Species) are very high ($>67\%$), implying that the taxonomy assignments from each reference database are fairly unique and are largely responsible for the differences observed in the co-occurrence networks generated from different taxonomy databases.
  The assignment between SILVA and the other two databases were originally significantly different ($40\%$ mismatch) even at the Phylum level, indicating that 40 of the top 100 assignments at the Phylum level in the SILVA database are different in SILVA.
  However, this was fixed by making minor adjustments to the taxonomic names, such as changing Bacteroidota to Bacteroidetes in the SILVA Phylum assignments.
  The comparison of all assigned genera (Figure~\ref{fig:figure_s5}) instead of the just the top 20 contains a higher percentage of mismatches.
  This suggests that the most abundant sequences are the ones that are consistently matched to the same taxonomies in the different reference databases, at least for the dataset tested in the current analysis.

@@

  Given that no database performs better than others against mock datasets, the choice of which database to use should be driven by other reasons.
  One user-specific way to choose, would be based on the known representation of taxa for the microbiome of interest (see also Discussion). Another reason could be the frequency of updates and the potential for future growth.
  % TODO: Find reference for this
  Since the \ac{gg} database is more widely used in the field~[ref], to enable easier comparison with published networks in literature, we set \ac{gg} as the \ac{micone} standard for taxonomy assignment.
  On the other hand, since the degree of similarity of assignments between \ac{ncbi} and \ac{gg} is fairly high, and due to its regular updation and maintenance the \ac{ncbi} database is also a good choice for the user.

>>>>

  In order to analyze the effect of different statistical methods on the inferred co-occurrence networks, we generated co-occurrence networks using all possible combinations of methods and estimated the variability in the networks due to each choice (Figure \ref{fig:figure2}A).
  This analysis and all subsequent analysis, unless explicitly mentioned, are performed on all the samples in the fecal microbiome transplant study.
  The networks are filtered on both association strength (0.1) and pvalue (0.05, only correlation methods) before the networks are subjected to the analyses.
  The effects of various steps on the final co-occurrence network is estimated by building a linear model of the edges of the network as a function the various step in the analysis pipeline (see Methods).
  Figure \ref{fig:figure2}A, shows the percentage of total variation among the co-occurrence networks due to the different steps of the pipeline.
  The TA step, more specifically, the choice of 16S reference database contributes the most ($\sim65.4\%$) to the variation in the networks, followed by the OP step ($\sim26.8\%$).
  This result highlights the importance of the taxonomy assignment step in the 16S data analysis workflow, implying that a change in the reference database will result in drastically different inferred networks.
  The reason for this seems to derive from the differential labeling of constitutive representative sequences into taxonomic entities (Figure~\ref{fig:figure4} and Figure~\ref{fig:figure_s5}), which drastically alter the nodes and hence the underlying network topology.
  In fact the variability induced by taxonomy assignment is much more significant than that due to the variability induced based on how the reference sequences themselves are identified (in the DC step).
  The residual variation (Figure \ref{fig:figure2}A) can be seen as an artifact that arises when multiple steps are changed at the same time, however this is small.

@@

  After assigning all the representative sequences to taxonomies we perform a pairwise comparison of the similarity between the top 100 assignments (by abundance) from different databases at every taxonomic level (Figure~\ref{fig:figure4}B).
  The assignments beyond Family level (Family, Genus and Species) are very dissimilar with $<45\%$ similarity between any pair of databases.
  The matches and mismatches in the assignments from all three databases are comparable, with \ac{ncbi} and SILVA being the most similar across most of the taxonomic levels, followed closed by \ac{gg} vs. SILVA.
  However, the number of mismatches for taxonomy assignments beyond the Genus level (Genus, Species) are very high ($>67\%$), implying that the taxonomy assignments from each reference database are fairly unique and are largely responsible for the differences observed in the co-occurrence networks generated from different taxonomy databases.
  The assignment between SILVA and the other two databases were originally significantly different ($40\%$ mismatch) even at the Phylum level, indicating that 40 of the top 100 assignments at the Phylum level in the SILVA database are different in SILVA.
  However, this was fixed by making minor adjustments to the taxonomic names, such as changing Bacteroidota to Bacteroidetes in the SILVA Phylum assignments.
  The comparison of all assigned genera (Figure~\ref{fig:figure_s5}) instead of the just the top 100 contains a higher percentage of mismatches.
  This suggests that the most abundant sequences are the ones that are consistently matched to the same taxonomies in the different reference databases, at least for the dataset tested in the current analysis.

@@

  Given that no database performs better than others against mock datasets, the choice of which database to use should be driven by other reasons.
  One user-specific way to choose, would be based on the known representation of taxa for the microbiome of interest (see also Discussion). Another reason could be the frequency of updates and the potential for future growth.
  % TODO: Find reference for this
  Since the \ac{gg} database is more widely used in the field~[ref], to enable easier comparison with published networks in literature, we set \ac{gg} as the \ac{micone} standard for taxonomy assignment.
  On the other hand, since the degree of similarity of assignments between \ac{ncbi} and \ac{gg} is fairly high (Figure~\ref{fig:figure_s5}), and due to its regular updation and maintenance the \ac{ncbi} database is also a good choice for the user.

### 2022-04-22 sections/supplementary.tex
Add: Script to generate Figure S5
Change: Update TA section with supplementary info

  \subsection*{}

>>>>

  \subsection*{Mismatches in all assignments at the \ac{TA} step}

    % TODO: Elaborate on this and work on the caption
    Figure~\ref{fig:figure_s5} is similar to Figure~\ref{fig:figure4}B, but instead of the matching only the top 100 taxonomic entities (by abundance), we match all the assignments from one database with those from the other two databases.
    We observe that the percentage of mismatches are indeed higher when considering all the assignments, implying that matching of the taxonomies in the more abundant sequences are more consistent.

    \begin{figure}[H]
      \centering
      \includegraphics[width=1.0\linewidth]{figure_s5.pdf}
    \end{figure}
    \begin{figure}[H]
      \centering
        \caption{
        }
      \label{fig:figure_s5}
    \end{figure}
    \FloatBarrier
    \newpage
